---
title: "Allan Variance Linear Regression Estimator Example"
author: "Gaetan Bakalli"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Beforehand, we need to load the following packages:

```{r, include=T}
library(av)
```
## Data Analysis

To understand the capabilities of the `avar` packages, we are going to analyze data coming from the `imudata` package, specificaly from a Adis 16405 IMU Gyroscope Y-axis, for which the Allan-deviation representation is given in the following figure:

```{r, fig.height = 7, fig.width = 7, fig.align = 'center', fig.cap = "Allan Variance Representation Adis 16405 IMU Gyroscope Y-axis."}
set.seed(2710)

# Select the axis
n = 100000
data = rnorm(n, 0, 0.01) +  cumsum(rnorm(n, 0, 3.162278e-05))

# Compute the Maximum-Overlap Allan Variance
allan_variance = avar(data, type = "mo")

# Log-Log representation of the Allan Variance
plot(allan_variance)
```

Based on this graph, we can see that our model should include a White Noise (WN) process for the 12 first scale wether we will consider a Random Walk (RW) for the remaining ones. 

```{r, warning = F}
# Specify the scale at which we want to fit the WN and RW process
wn = 1:7
rw = 13:15

# Compute the Allan Variance Linear Regression Estimator (AVLR)
fit = avlr(allan_variance, wn = wn, rw = rw)
fit
```

Now that we have computed the parameters of interest, we can see graphically if the choosen latent model fits well the data at hand:

```{r, fig.height = 7, fig.width = 7, fig.align = 'center', fig.cap = "Empirical AV with AV implied by the latent model WN + RW"}
plot(fit)
plot(fit, decomp = T)
```

As we can see, the model fits the data well, therefore, we are going to compute the confidence intervals for those parameter through the option `ci = TRUE`.

```{r, warning = F, eval = F}
# AVLR estimator with 95% confidence intervals
fit_ci = avlr(allan_variance, wn = 1:7, rw = 13:15, ci = TRUE, B = 100)
```
