---
title: "Allan Variance Linear Regression Estimator Example"
author: "Gaetan Bakalli"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Allan Variance Linear Regression Estimator Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Beforehand, we need to load the following package:

```{r, include=T}
library(avar)
```

## Data Analysis

To understand the capabilities of the `avar` package, we are going to use simulated data of sample size $n = 10^5$. The corresponding Allan Variance representation is given in the following figure: 

```{r, fig.height = 7, fig.width = 7, fig.align = 'center', fig.cap = "Allan Variance Representation."}
set.seed(2710)

# Simulate data
n = 100000
data = rnorm(n, 0, 0.01) +  cumsum(rnorm(n, 0, 3.162278e-05))

# Compute the Maximum-Overlap Allan Variance
allan_variance = avar(data, type = "mo")

# Log-Log representation of the Allan Variance
plot(allan_variance)
```

Based on this graph, we can see that our model should include a White Noise (WN) process for the first 7 scales and we will consider a Random Walk (RW) process for the last 3 scales.

```{r, warning = F}
# Specify the scale at which we want to fit the WN and RW processes
wn = 1:7
rw = 13:15

# Compute the Allan Variance Linear Regression Estimator (AVLR)
fit = avlr(allan_variance, wn = wn, rw = rw)
fit
```

Now that we have computed the parameters of interest, we can see graphically if the chosen latent model fits the data at hand well:

```{r, fig.height = 7, fig.width = 7, fig.align = 'center', fig.cap = "Empirical AV with AV implied by the latent model WN + RW"}
plot(fit)
plot(fit, decomp = T)
```

As we can see, the model fits the data well. Therefore, we are going to compute the confidence intervals for those parameters through the option `ci = TRUE`.

```{r, warning = F, eval = F}
# AVLR estimator with 95% confidence intervals
fit_ci = avlr(allan_variance, wn = 1:7, rw = 13:15, ci = TRUE, B = 100)
fit_ci$ci
```


```{r, warning = F, echo = F, eval = T}
load("fit_ci.rda")
fit_ci$ci
```
